---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# prebaked

<!-- badges: start -->
<!-- badges: end -->

The goal of the prebaked package is to provide a function called count_all_missing_by_group that allows users to count all of the values within all of the columns in a dataset that are missing and display the missing values grouped by a specific column. This package uses the dplyr package from the tidyverse, so make sure you are calling the tidyverse before you try to use this package.

## Installation

You can install the development version of prebaked like so:

``` r
install_github("gracem25/prebaked", ref = "0.1.0")
```

## Usage

This is a basic example which shows you how to solve a common problem:

```{r example}

# the problem? I want to figure out how many missing values I have within each column of the core R dataset airquality and group them by the month in which they occurred.

library(prebaked)
library(tidyverse)

count_all_missing_by_group(airquality, Month)

airquality |> count_all_missing_by_group(Month)

count_all_missing_by_group(airquality, Month, .groups = "keep")

```

